Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-21 methods-and-results.Rmd
clustering info added

\begin{itemize}
  \item feature selection
  \begin{itemize}
    \item filter: evaluate individual features' impact / importance / relevance. Univariate (ranking-based) or multivariate (preferred bc. can handle redundant and irrelevant features)
    \begin{itemize}
      \item unvariate, often based on information or spectral analysis (univariate inclusion test \citep[i.e., alpha-corrected t-tests][]{christ2018})
    \end{itemize}
    \item wrapper: search problem --- compare different models based on evaluation criterion (i.e., model performance; e.g., $R^2$, accuracy, ...). "high computational cost, and they are limited to be used in conjunction with a particular clustering algorithm."
    \begin{itemize}
      \item Exhaustive Feature Selection (i.e., brute force)
      \item forward selection (e.g., greedy Forward Search \citep[][]{wang2006})
      \item backward elimination
      \item Bi-directional elimination (Stepwise Selection)
    \end{itemize}
    \item hybrid: first filter then wrapper
    \item [embedded: feature selection as part of the model construction process. E.g., LASSO Regularization L1, or Random Forest Importance] MOSTLY FOR SUPERVISED / LABELED DATA (e.g., regressions)
  \end{itemize}
  \item dimension reduction
\end{itemize}

@@

>>>>

\begin{itemize}
  \item dimension reduction
  \item feature selection
  \begin{itemize}
    \item filter: evaluate individual features' impact / importance / relevance. Univariate (ranking-based) or multivariate (preferred bc. can handle redundant and irrelevant features)
    \begin{itemize}
      \item unvariate, often based on information or spectral analysis (univariate inclusion test \citep[i.e., alpha-corrected t-tests][]{christ2018})
    \end{itemize}
    \item wrapper: search problem --- compare different models based on evaluation criterion (i.e., model performance; e.g., $R^2$, accuracy, ...). "high computational cost, and they are limited to be used in conjunction with a particular clustering algorithm."
    \begin{itemize}
      \item Exhaustive Feature Selection (i.e., brute force)
      \item forward selection (e.g., greedy Forward Search \citep[][]{wang2006})
      \item backward elimination
      \item Bi-directional elimination (Stepwise Selection)
    \end{itemize}
    \item hybrid: (usually) first filter then wrapper (e.g., Bayesian Filter KMeans)
    \item [embedded: feature selection as part of the model construction process. E.g., LASSO Regularization L1, or Random Forest Importance] MOSTLY FOR SUPERVISED / LABELED DATA (e.g., regressions)
  \end{itemize}
\end{itemize}

@@

\subsection{Clustering}

\begin{itemize}
  \item centroid-based (e.g., k-means)
  \begin{itemize}
    \item non-probabilistic
    \item no assumptions
    \item fast
    \item sensitive to local minima
  \end{itemize}
  \item distribution-based (e.g., gaussian mixture model [GMM])
  \begin{itemize}
    \item probabilistic
    \item (gaussian) distributions assumed
    \item more flexible shape than vanilla centroid-based
  \end{itemize}
  \item density-based (e.g., dbscan)
  \begin{itemize}
    \item no shape assumption
    \item do not assign outliers (i.e., outlier detection)
  \end{itemize}
  \item Hierarchical-based (e.g., Ward hierarchical clustering)
  \begin{itemize}
    \item divisive (top-down) and agglomerative (bottom-up)
    \item no pre-specified number of clusters
    \item easy visual inspection (dendogram)
    \item best for small number of cases
    \item no reversal of assignments
  \end{itemize}
  \item Hybrid (e.g, GMM with kmeans centroids as starting point)
  \begin{itemize}
    \item helps avoid individual shortcomings (e.g., local minima avoidance)
  \end{itemize}
\end{itemize}
